---
title: "Lab 1 - Data visualization"
author: "Emanuel Lopez Gallegos"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(viridis)
```
```{r}
view(midwest)
```

## Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)
```{r ex-1}
#| label: Ex-1
ggplot(data = midwest, 
       mapping = aes(x = popdensity)) +
  geom_histogram(alpha = 1, binwidth = 10000) + 
  labs(
    x = "Population density",
    y = "Count", 
    title = "Population Densities of the Midwest"
  )
```
The distribution is skewed to the right. 

Above, we can see some data in between the bin of 75000 and 100000, which is far from most of the data sitting near 0.

## Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)
```{r}
scale_color_viridis_d()
```

```{r}
ggplot(data = midwest, 
       mapping = aes(x = percollege, y = percbelowpoverty, color = state)) +
  scale_color_viridis_d() +
  geom_point() + 
  labs(
    x = "PercOfPeople w/College Degree",
    y = "PercOfPeople Below Poverty", 
    title = "% College Degrees v. % Below Poverty "
  ) 
```
## Exercise 3

What I observe is that there is a negative association, but not too extreme. Almost all of the states have a great distribution of counties where the percent of college degrees is between 10-30 percent havea percentage of people below the poverty line between 5-20 percent. 

## Exercise 4

## Exercise 5

## Exercise 6

## Exercise 7
