---
title: "Lab 1 - Data visualization"
author: "Emanuel Lopez Gallegos"
format: pdf
editor: visual
---

## Load Packages

```{r}
#| label: load-packages
#| message: false

library(tidyverse)
library(viridis)
```
```{r}
view(midwest)
```

## Exercise 1

(Type your answer to Exercise 1 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)
```{r}
ggplot(data = midwest, 
       mapping = aes(x = popdensity)) +
  geom_histogram(alpha = 1, binwidth = 10000) + 
  labs(
    x = "Population density",
    y = "count"
  )
```
The distribution is skewed to the right. 

Above, we can see some data in between the bin of 75000 and 100000, which is far from most of the data sitting near 0.

## Exercise 2

(Type your answer to Exercise 2 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

## Exercise 3

(Type your answer to Exercise 3 here. Add code chunks as needed. Don't forget to label your code chunk. Do not use spaces in code chunk labels.)

## Exercise 4

## Exercise 5

## Exercise 6

## Exercise 7
